---
title: "Price_Prediction_Initial_Draft"
date: "2023-05-01"
author: "Anish Gupta"
output:
  html_document:
   toc: true
   toc_depth: 2
   toc_float:
      collapsed: true
      smooth_scroll: false
editor_options:
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(ggplot2)
library(scales)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(plotly)
library(countrycode)
library(corrplot)
library(RColorBrewer)
library(ggmap)
library(rpart)
library(rpart.plot)
library(ISLR)
library(leaps)
library(lars)
library(moderndive)
library(randomForest)
library(caret)
library(Metrics)
library(reshape2)
library(xgboost)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```
# Prepare Data

## Read the data
```{r}
airbnb_original <- read_csv("airbnb_eda.csv")
glimpse(airbnb_original)
```

## Feature Engineering: Part 1
```{r}
#Summary of airbnb
summary(airbnb_original)

#Convert neighbourhood_group, neighborhood and room_type to factor.
airbnb_original$neighbourhood_group<- as.factor(airbnb_original$neighbourhood_group)
airbnb_original$neighbourhood<- as.factor(airbnb_original$neighbourhood)
airbnb_original$room_type<- as.factor(airbnb_original$room_type)

airbnb_original %>% 
     sapply(levels)

#Create new numeric variables from the factor variables neighbourhood_group, neighborhood and room_type to factor.
airbnb_original <- airbnb_original %>%
  mutate(neighbourhood_group_numeric=ifelse(neighbourhood_group == "Bronx", 1, ifelse(neighbourhood_group == "Brooklyn",2,ifelse(neighbourhood_group == "Manhattan",3,ifelse(neighbourhood_group == "Queens",4,5)))))

airbnb_original <- airbnb_original %>%
  mutate(room_type_numeric=ifelse(room_type == "Entire home/apt",1,ifelse(room_type == "Private room",2,3)))

airbnb_original <- airbnb_original %>%
  mutate(neighbourhood_numeric=as.numeric(neighbourhood))

#Convert last_review date to a date format.
airbnb_original <- airbnb_original %>%
  mutate(last_review = ifelse(is.na(last_review),"01/01/2000",last_review))%>%
  mutate(last_review = mdy(last_review))

#Replacing NA values for reviews_per_month with 0.
airbnb_original <- airbnb_original %>%
  mutate(reviews_per_month = ifelse(is.na(reviews_per_month), 0, reviews_per_month))
```
## Feature Engineering: Part 2
```{r}
#Drop columns that will not be useful in the price prediction
#name: The name of the host cannot have any impact on the price prediction
#host_id: It is just an id assigned to a host. It does not have any impact on the price
#last_review: The last review column is being dropped as it may not have an impact on price. 
#Location: It is the address of the place and since we are using latitude and longitude, I feel this is not needed to predict the price.
#View(airbnb_original)

airbnb <- airbnb_original %>%
  select(-name, -host_id, -host_name, -last_review, -Location)
```

## Feature Engineering Part 3
```{r}
#summary of airbnb variables
summary(airbnb)

#Checking for and removing outliers
airbnb %>%
  select_if(is.numeric) %>%
  select(-id) %>%
  gather(yval, val, -price) %>%
  ggplot(aes(price, val)) +
  geom_point() +
  facet_grid(yval~.)

airbnb <- subset(airbnb, airbnb$price > 0 & airbnb$price < 7500)

airbnb %>%
  ggplot(aes(price,number_of_reviews))+
  geom_point()

airbnb %>%
  ggplot(aes(price,reviews_per_month))+
  geom_point()

airbnb <- subset(airbnb, airbnb$reviews_per_month < 30)

airbnb %>%
  ggplot(aes(price,minimum_nights))+
  geom_point()

airbnb <- subset(airbnb, airbnb$minimum_nights < 600)
```

## Feature Engineering Part 4
```{r}
#Create Plots to check the relationship between Price and the other variables and apply transformations where necessary
airbnb %>%
  ggplot(aes(x=price)) + geom_histogram(color="white")

airbnb %>%
  ggplot(aes(x=log(price))) + geom_histogram(color="white")

airbnb%>%
  ggplot(aes(x=minimum_nights)) + geom_histogram(color="white")

model1 <- lm(data=airbnb, price ~ minimum_nights )
get_regression_table(model1)

points<-get_regression_points(model1)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()

#Transforming the price and minimum nights to log form as they are right skewed.
airbnb<-airbnb %>%
  mutate(lnprice=log(price), lnmin_nights=log(minimum_nights))

ggplot(data=airbnb, aes(x=lnprice)) + geom_histogram(color="white")
ggplot(data=airbnb, aes(x=lnmin_nights)) + geom_histogram(color="white")

head(airbnb)
model1 <- lm(data=airbnb, lnprice ~ lnmin_nights)

get_regression_table(model1)

points<-get_regression_points(model1)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=lnprice_hat, y=residual)) + geom_point()

#Create some tables and some boxplots for the factor variables
table(airbnb$neighbourhood_group)
table(airbnb$neighbourhood)
table(airbnb$room_type)

ggplot(data=airbnb, aes(y=lnprice,fill= neighbourhood_group)) + geom_boxplot()
ggplot(data=airbnb, aes(y=lnprice,fill=room_type)) + geom_boxplot()
ggplot(data=airbnb, aes(y=lnprice,fill=neighbourhood)) + geom_boxplot()

#Creating scatterplots for the numeric variables
ggplot(data=airbnb, aes(x=lnmin_nights, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=longitude, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=latitude, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=floor, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=`noise(dB)`, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=number_of_reviews, y=lnprice)) + geom_point()
ggplot(data=airbnb, aes(x=reviews_per_month, y=lnprice)) + geom_point()
#Running the lnprice vs number_of_reviews resulted in a cone shaped graph and so plotting against log(number_of_reviews)
ggplot(data=airbnb, aes(x=log(number_of_reviews), y=lnprice)) + geom_point()
#Running the lnprice vs reviews_per_month resulted in a cone shaped graph and so plotting against log(reviews_per_month)
ggplot(data=airbnb, aes(x=log(reviews_per_month), y=lnprice)) + geom_point()
```



## Feature Engineering Part 5
```{r}
#Create a numeric dataframe for models that require numeric only or perform better with numeric variables
airbnb_numeric <- airbnb %>%
  select(-neighbourhood_group,-neighbourhood,-room_type)
```



## Checking to see how a model works with and without the log transformed variables
```{r}
model0<-lm(price~neighbourhood_group + neighbourhood+ latitude + longitude + room_type + number_of_reviews + reviews_per_month + floor + `noise(dB)` + minimum_nights,airbnb)

get_regression_summaries(model0)
get_regression_table(model0)
points<-get_regression_points(model0)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()

model1 <- lm(data=airbnb, lnprice ~ neighbourhood_group +neighbourhood+ latitude + longitude + room_type + number_of_reviews + reviews_per_month + floor + `noise(dB)` + lnmin_nights )
get_regression_table(model1)

get_regression_summaries(model1)
points<-get_regression_points(model1)
points
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=lnprice_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()

```

# Visualize Correlation Matrix
```{r}
glimpse(airbnb_numeric)

corrplot(cor(airbnb_numeric[,-1]))
```

# Modeling

## Split the dataset into test and train.
```{r}
#make this example reproducible
set.seed(1)

#use 70% of dataset as training set and 30% as test set
sample <- sample(c(TRUE, FALSE), nrow(airbnb), replace=TRUE, prob=c(0.7,0.3))
airbnb_train  <- airbnb[sample, ]
airbnb_test   <- airbnb[!sample, ]

#The following R code sets all observations in our test data set to NA that contain the additional level that didn’t exist in our train data:
airbnb_test_new <- airbnb_test                                # Duplicate test data set
airbnb_test_new$neighbourhood[which(!(airbnb_test_new$neighbourhood %in% unique(airbnb_train$neighbourhood)))] <- NA  # Replace new levels by NA
airbnb_test_new 

#use 70% of dataset as training set and 30% as test set
sample_numeric <- sample(c(TRUE, FALSE), nrow(airbnb_numeric), replace=TRUE, prob=c(0.7,0.3))
airbnb_train_numeric  <- airbnb_numeric[sample_numeric, ]
airbnb_test_numeric   <- airbnb_numeric[!sample_numeric, ]

#Get the train and test ID
train_id <- data.frame(ID = airbnb_train_numeric$id)
test_id  <- data.frame(ID = airbnb_test_numeric$id)

#Dropping the Id columns
airbnb_train_numeric <- airbnb_train_numeric[,-1]
airbnb_test_numeric  <- airbnb_test_numeric[,-1]

#Creating X train and test datasets and Y train and test datasets for the random forest model
X_train <- airbnb_train_numeric[, -c(3,12,13)]#Drop the dependent variables which are price and lnprice and create the X_train dataframe.
Y_train <- airbnb_train_numeric[, 3]#Select the price and create the Y_train dataframe.

X_test <- airbnb_test_numeric[, -c(3,12,13)]#Drop the dependent variables which are price and lnprice and create the X_test dataframe.

Y_test <- airbnb_test_numeric[, 3]#Select the price and create the Y_test dataframe.

#The following steps are specifically for the xgboost model
#Change target variable as a numeric vector and the rest of train dataset into matrix form.
train_mat<-as.matrix(X_train)
mode(train_mat)<-'double' #coerce categorical variables to change to numeric.

#Change target variable as a numeric vector and the rest of test dataset into matrix form.
test_mat<-as.matrix(X_test)
mode(test_mat)<-'double' #coerce categorical variables to change to numeric.
```

## Model 1: OLS Linear Regresssion
```{r}
model.ols<-lm(price ~ neighbourhood_group + neighbourhood+latitude + longitude + room_type + number_of_reviews + floor + `noise(dB)` + minimum_nights +  room_type*neighbourhood_group+ floor*neighbourhood_group + floor*room_type+  neighbourhood*floor+ room_type*neighbourhood+ neighbourhood_group*neighbourhood,airbnb_train)


get_regression_summaries(model.ols)
get_regression_table(model.ols)
points<-get_regression_points(model.ols)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()


airbnb.predictions <- predict(model.ols,airbnb_test_new)
#airbnb.predictions

#result_test <- data.frame(ID = airbnb_test_new$id,
                           #price = exp(airbnb_test_new$lnprice),
                    #predictions = exp(airbnb.predictions))

result_test <- data.frame(ID = airbnb_test_new$id,
                          price = airbnb_test_new$price,
                          predictions = airbnb.predictions)
write.csv(result_test,file = "C:/Users/anish/Documents/Data Science Capstone/predicitions_airbnb_ols.csv")

```


## Model 2 AIC
```{r}
null <- lm(price~1, data = airbnb_train)
full <- lm(price ~ neighbourhood_group +neighbourhood+ latitude + longitude + room_type + number_of_reviews + reviews_per_month + floor + `noise(dB)` + minimum_nights, data = airbnb_train)

step(null, scope =list(lower=null, upper= full), direction = "both")


airbnb_model_aic<-lm(formula = price ~room_type + neighbourhood + floor + `noise(dB)` + 
    number_of_reviews + longitude, data = airbnb_train)

get_regression_summaries(airbnb_model_aic)
get_regression_table(airbnb_model_aic)
points<-get_regression_points(airbnb_model_aic)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()


airbnb.predictions <- predict(airbnb_model_aic,airbnb_test_new)
#airbnb.predictions

```

## Model 3 Random Forest
```{r}
#Run the random forest model
randomforest_model <- randomForest(price~neighbourhood_group_numeric +neighbourhood_numeric+ latitude + longitude + room_type_numeric + minimum_nights  + number_of_reviews + floor  + minimum_nights,data = airbnb_train_numeric)

# View the forest results.
print(randomforest_model) 

# Importance of each predictor.
print(importance(randomforest_model,type = 2)) 

#Predict the price based on X_train.
pred_train <- predict(randomforest_model, X_train)

#Create a dataframe with the train_id, the actual price, and the predicted price. 
result_train <- data.frame(ID = train_id, 
                     price = Y_train,
                    predictions = pred_train)
#Print the head of the dataframe result_train.
head(result_train)


#Predict the price based on X_test.
pred_test <- predict(randomforest_model, airbnb_test_numeric)

#Create a dataframe with the test_id, the actual price, and the predicted price. 
result_test <- data.frame(ID = test_id, 
                          price = Y_test,
                    predictions = pred_test)


write.csv(result_test,file = "C:/Users/anish/Documents/Data Science Capstone/predicitions_airbnb_rf.csv")
#Print the head of the dataframe result_train.
head(result_test)

print(paste0('Test RMSE: ' , rmse(result_test$price,
                                  result_test$predictions))) #testRMSE

print(paste0('Train RMSE: ' , rmse(result_train$price,
                                  result_train$predictions))) 

print(paste0('Test R2: ' ,
             caret::postResample(result_test$predictions , result_test$price)['Rsquared']))

print(paste0('Train R2: ' ,
             caret::postResample(result_train$predictions , result_train$price)['Rsquared']))


ggplot(result_test, aes(x = predictions, y = price)) + geom_point() +
  geom_smooth()

melt_pred_test <- melt(head(result_test,20), id.vars = "ID")

ggplot(melt_pred_test, 
       aes(y = value, 
           x = ID,
           colour = variable)) +
      geom_point() +
      geom_line() +
  ggtitle("Actual vs Predicted for Test Data")


```

## Model 4: Extreme Gradient Boosting(XG Boost)
```{r}
#Preparing two matrices for xgb
dtrain <- xgb.DMatrix(data = train_mat, label = airbnb_train_numeric$price)
dtest <- xgb.DMatrix(data = test_mat, label = airbnb_test_numeric$price)

#Run xgboost
bst <- xgboost(data = dtrain, max.depth = 5, eta = 1, nround = 1000)
bst

#Generate prediction on the test dataset with the model.
preds <- predict(bst, dtest)
#preds

#Calculate RMSE
err <- preds-airbnb_test_numeric$price
rmse <- sqrt(sum(err)^2/nrow(airbnb_test_numeric))

#Create a dataframe with the test_id, the actual price, and the predicted price. 
result_test <- data.frame(ID = test_id, 
                     price = airbnb_test_numeric$price,
                    predictions = preds)

#Print the results 
print(paste("test-error=", rmse))

print(paste0('Test R^2: ' ,
             caret::postResample(result_test$predictions , result_test$price)['Rsquared']))

#On Test Data Change to Pivot longer.
melt_pred_test <- melt(head(result_test,100), id.vars = "ID")

ggplot(melt_pred_test, 
       aes(y = value, 
           x = ID,
           colour = variable)) +
      geom_point() +
      geom_line() +
  ggtitle("Actual vs Predicted for Test Data")

```



## Model 5: Leaps and Lars Model


### Function to build second order matrix for x variables
```{r}
#Builds second order terms for x values.
matrix.2ndorder.make<-function(x, only.quad=F){
  x0<-x
  dimn<-dimnames(x)[[2]] #extract the names of the variables
  num.col<-length(x[1,]) # how many columns
  for(i in 1:num.col){
    # if we are doing all 2nd order
    if(!only.quad){
      for(j in i:num.col){
        x0<-cbind(x0,x[,i]*x[,j])
        dimn<-c(dimn,paste(dimn[i],dimn[j],sep=""))
        #create interaction dimension names

      }
    }
    else{
        #in here only if doing only squared terms
        x0<-cbind(x0,x[,i]*x[,i])
        dimn<-c(dimn,paste(dimn[i],"2",sep="")) # squared dimension names
    }
  }
  dimnames(x0)[[2]]<-dimn
  x0
}

```


### A Leaps automatic model selector using Cp, and PRESS
### Best k models using Cp and from those k calculate best PRESS

### Leaps then Press
```{r}
#names function, takes two variables
regpluspress<-function(x,y){
 str<-lsfit(x,y) #Saves lsfit output to str.
 press<-sum((str$resid/(1-hat(x)))^2)
str$press<-press #Saves PRESS statistic to str
str #Calls str
}
#Takes parameters
leaps.then.press<-function(xmat,yvec,ncheck=10,print.ls=F)
{
    leaps.str<-leaps(xmat,yvec) #Runs through leaps and saves output to leaps.str
    z1<-leaps.str$Cp #extract Cp
    o1<-order(z1) #Order it
    matwhich<-(leaps.str$which[o1,])[1:ncheck,] #pullout ncheck best models with respect to Cp.
    z2<-z1[o1][1:ncheck] #Saves lowest cp values to z2
    pressvec<-NULL
    for(i in 1:ncheck){ #A for loop from 1 to number of checks
      ls.str0<-regpluspress(xmat[,matwhich[i,]],yvec) #Saves PRESS statistics from lowest Cp list 
      if(print.ls){#If called, then it will print ls.str0
          ls.print(ls.str0)
      }
      print(i) #Prints iteration
      print(paste("Press=",ls.str0$press)) #Prints PRESS stat
      parvec<-matwhich[i,] #Saves matrix row to vector
      npar<-sum(parvec) #Sums vector values to npar (sums 1 and 0 values) 
      print(paste("MPSE=",ls.str0$press/(length(yvec)-(npar+1)))) #Prints the mean squared prediction error
      print(paste("Cp=",z2[i])) #Prints Cp value
      pressvec<-c(pressvec, ls.str0$press)
      if(i==1){
        Xmat<-(xmat)[,leaps.str$which[o1[1],]]
        coef1<-lsfit(Xmat,yvec)$coef
        print("coef1=")
        print(coef1)
        leaps.pred<-Xmat%*%coef1[-1]+coef1[1]
        plot(leaps.pred,yvec)
        print("Correlation between leaps prediction and actual yvec")
        print(cor(leaps.pred,yvec))
      }
    }
    o2<-order(pressvec) #Output results
    print("which matrix:")
    matwhich[o2,] #model indicators sorted from best press to worst in top ncheck Cp
    print("matwhich 1")
    matwhich[o2[1]]
        
}

```

### And a lars automatic model selector using both Cp and cross validation MSE
### lars selection program
```{r}
#Function to generate sum of the absolute values of a vector.
sumabs<-function(v1)
{sum(abs(v1))}

#lars select function. This is a lars automatic model selector using both Cp and cross validation MSE
lars.select<-
function(xmat,y,ncheck=10,int=F)
{
        lasso.str<-lars(xmat,y,intercept=int) #Calls lars, saves output to lasso.str
        #plot(lasso.str)
        #print(xmat)
        cv.str<-cv.lars(xmat,y,plot.it=F,intercept=int) #Calculates cross-validated error curve for lars
        o1<-order(cv.str$cv) #Orders cv values from lowest to highest
        mindex<-cv.str$index[o1][1] #Index of cv values ordered
        beta<-coef(lasso.str) #Saves coefficients from lasso.str to beta
        index0<-apply(beta,1,sumabs) #Iterates through rows, sums absolute values of beta (sum of squares)
        index0<-index0/max(index0) #Sums of beta divided by max sum of beta, percentage (0 to 1)
        o1<-order(abs(index0-mindex)) #Orders values subtracted by the minimum cv value
        I1<-(abs(index0-mindex)==min(abs(index0-mindex)))#If absolute value of index-mindex is the min, add to I1
        n1<-length(beta[,1]) #Saves int, length of column of coefficients
        beta.out<-beta[I1,] #Beta.out is minimum rows of coefficients
        if(sum(abs(beta.out))==0){ #If all values add to zero, then sort list by the Cp value
                v1<-lasso.str$Cp
                o2<-order(v1)
                beta.out<-beta[o1[1:ncheck],]
        }
        Ind.out<-beta.out!=0 #Saves Ind.out as values of beta.out that don't equal 0
        outlist<-list(beta.out=beta.out,ind.out=Ind.out)#Saves list of beta.out, ind.out values
        if(int){#finds y-intercept values.
                Int.out1<-mean(y)-mean(xmat%*%beta.out[i]) #mean of y-value minus mean of x-matrix times beta coefficients
                outlist<-list(beta.out=beta.out,ind.out=Ind.out,int.out=Int.out1)
        }       
        outlist #Returns outlist to end function
}

```


### Combine leaps and lars in a single function
```{r}
#Combine function calling leaps.then.press and lars.select
combined.leaps.lars<-function(both = F,leaps = F, lars = F,xmat,yvec,ncheck=10,int=F)
{ 
 #if(both==TRUE){par(mfrow=c(2,1))}else{par(mfrow=c(1,1))}
 if(both){
    leaps.output<-leaps.then.press(xmat,yvec,ncheck,int)
    lars.output<-lars.select(xmat,yvec)
    plot(xmat%*%lars.output$beta.out,yvec) #Actual Price vs predicted Price
    print("Correlation between predicted Price and actual Price Lars")
    print(cor(xmat%*%lars.output$beta.out,yvec)) #correlation
    #Combine leaps and lars output in a list 
    lars.leaps.output<-list(leaps.output=leaps.output,lars.output=lars.output)
    #Return the output
    lars.leaps.output
 }
  else if(leaps){
    leaps.output<-leaps.then.press(xmat,yvec,ncheck,int)
    leaps.output
  }
  else if(lars){
    lars.output<-lars.select(xmat,yvec)
    plot(xmat%*%lars.output$beta.out,yvec) #Actual Price vs predicted Price
    print("Correlation between predicted Price and actual Price Lars")
    print(cor(xmat%*%lars.output$beta.out,yvec)) #correlation
    lars.output
  }
  

}
```

### Build second order matrix

```{r}
#Creating a matrix from the data
airbnb_numeric_mat<-as.matrix(airbnb_numeric)
#Output the first 5 rows
airbnb_numeric_mat[1:5,]

#Linear fit
ls.print(lsfit(airbnb_numeric_mat[,c(-3,-11)],airbnb_numeric_mat[,3]))
# From the linear fit we can see that  reviews_per_month is not a good predictor because p-value is greater than 0.05.


#Make second order matrix of the x values but drop id, price,lnprice,latitude, longitude,lnmin_nights, reviews_per_month,neighborhood
airbnb_numeric_mat2nd<-matrix.2ndorder.make(airbnb_numeric_mat[,c(-1,-2,-3,-4,-7,-13,-14,-12)])#Second order matrix for x variables
airbnb_numeric_mat2nd[1:5,]

#dim(airbnb_numeric_mat2nd)

```



### Call leaps and lars
```{r}
#Run combined.leap.lars function for full
results.leaps.lars<-combined.leaps.lars(both = F,leaps = T,lars = F,airbnb_numeric_mat2nd,airbnb_numeric_mat[,4])
#results.leaps.lars

#Run combined.leap.lars function for full 
results.leaps.lars<-combined.leaps.lars(both = F,leaps = F,lars = T,airbnb_numeric_mat2nd,airbnb_numeric_mat[,4])
#results.leaps.lars

#airbnb_numeric_mat

```


### Build the linear model on the output of leaps variable selection. Run predictions on the test data and write to a .csv file.
```{r}
linear.airbnb<-lm(price ~ minimum_nights +floor + `noise(dB)` + neighbourhood_group_numeric +  room_type_numeric + I(minimum_nights^2) + minimum_nights*floor +  minimum_nights*`noise(dB)` + minimum_nights*neighbourhood_group_numeric + minimum_nights*room_type_numeric + number_of_reviews*number_of_reviews + number_of_reviews*floor + number_of_reviews*neighbourhood_group_numeric + number_of_reviews*room_type_numeric + I(floor^2) + floor*`noise(dB)` + floor*neighbourhood_group_numeric + floor*room_type_numeric + I(`noise(dB)`^2) + `noise(dB)`*neighbourhood_group_numeric + `noise(dB)`*room_type_numeric + I(neighbourhood_group_numeric^2) + neighbourhood_group_numeric*room_type_numeric +  I(room_type_numeric^2), data = airbnb_train_numeric)


get_regression_summaries(linear.airbnb)
get_regression_table(linear.airbnb)
points<-get_regression_points(linear.airbnb)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()

airbnb.predictions <- predict(linear.airbnb,airbnb_test)
#write.csv(airbnb.predictions,file = "C:/Users/anish/Documents/predicitions_airbnb.csv")
```

### Build the linear model on the output of lars variable selection. Run predictions on the test data and write to a .csv file.
```{r}
linear.airbnb<-lm(price ~ minimum_nights + number_of_reviews + floor + `noise(dB)` + neighbourhood_group_numeric + room_type_numeric + I(minimum_nights^2) + minimum_nights*number_of_reviews + minimum_nights*floor + minimum_nights*`noise(dB)` + minimum_nights*neighbourhood_group_numeric +  minimum_nights*room_type_numeric + I(number_of_reviews^2) + number_of_reviews*floor + number_of_reviews*`noise(dB)` +  number_of_reviews*neighbourhood_group_numeric + number_of_reviews*room_type_numeric + I(floor^2) + floor*`noise(dB)` + floor*neighbourhood_group_numeric + floor*room_type_numeric + I(`noise(dB)`^2) + `noise(dB)`*room_type_numeric + I(neighbourhood_group_numeric^2) + neighbourhood_group_numeric*room_type_numeric + I(room_type_numeric^2), data = airbnb_train_numeric)

get_regression_summaries(linear.airbnb)
get_regression_table(linear.airbnb)
points<-get_regression_points(linear.airbnb)
ggplot(data=points, aes(x=residual)) + geom_histogram(color="white")
ggplot(data=points, aes(x=price_hat, y=residual)) + geom_point()
points %>%
  ggplot(aes(sample = residual)) +
  stat_qq() +
  stat_qq_line()
```


